Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-01 paper/disc20clustering.tex
No ground set respecting

We say that a component or a ground set is \emph{trivial}, if it contains exactly one node.
We say that the node that belongs to trivial component or a ground set is \emph{alone}.
We say that a~configuration is \emph{component respecting}
if the nodes belonging to the same component are collocated.
Similarly, we define a \emph{ground-set-respecting} configuration.

@@

We construct the ground sets in a way that they always form a balanced partition of nodes.
This way, the optimal algorithm moves to a~ground-set-respecting configuration, and serves all requests for free.
(This implies that the algorithm must eventually move to any ground-set-respecting configuration if it is competitive.)

>>>>

We say that a component or a ground set is \emph{trivial}, if it contains exactly one node.
We say that the node that belongs to trivial component or a ground set is \emph{alone}.
We say that a~configuration is \emph{component-respecting}
if the nodes belonging to the same component are collocated.

@@

We construct the ground sets in a way that they always form a balanced partition of nodes.
This way, the optimal algorithm moves to such a configuration, and serves all requests for free.\maciek{i can do better: such a?}
(This implies that the algorithm must eventually collocate nodes of a ground set to be competitive.)
